---
title: "Ryan Tillis - Data Science - Toolbox - Quiz 1 - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "June 3, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Scientist's Toolbox Quiz 1

This is Quiz 1 from the Data Scientist's toolbox course within the Data Science Specialization. This publication is intended as a learning resource, all answers are documented and explained.

###Questions
<hr>
<font size="+2">1.  </font> Which of the following are courses in the Data Science Specialization? Select all that apply.

<hr>

<font size="+1">

* Getting and Cleaning Data

* Developing Data Products

* R programming

</font>

<hr>

#####Explanation:

Self-explanatory

```{r Question 1}

```

<hr>

<font size="+2">2.  </font> Why are we using R for the course track? Select all that apply.

<hr>

<font size="+1">

* R is free.

* R has a large number of add on packages that are useful for data analysis.

* R has a nice IDE, Rstudio.

</font>

<hr>
```{r Question 2}

```

#####Explanation:

R is open source and has a great community and IDE.

<hr>

<font size="+2">3.  </font> What are good ways to find answers to questions in this course track? Select all that apply.

<hr>

<font size="+1">

* Searching Google.

* Posting to the course discussion forum

* Searching Stack Overflow

</font>

<hr>
```{r Question 3}

```

#####Explanation:

Self-explanatory

<hr>

<font size="+2">4.  </font> What are characteristics of good questions on the message boards? Select all that apply.

<hr>

<font size="+1">

* Is very specific.

* Is polite and courteous.

</font>

<hr>
```{r Question 4}

```

#####Explanation:

Self-explanatory

<hr>

<font size="+2">5.  </font> Which of the following packages provides machine learning functionality? Select all that apply

<hr>

<font size="+1">

* kernlab

* pamr

* rpart

</font>

<hr>
```{r Question 5}

```

#####Explanation:

Check Here: <http://www.kdnuggets.com/2015/06/top-20-r-machine-learning-packages.html> for a more comprehensive list.

<hr>
Check out my website at: <http://www.ryantillis.com/>
