---
title: "Ryan Tillis - Data Science - Toolbox - Quiz 1 - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "June 6, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Scientist's Toolbox Quiz 1

This is Quiz 2 from the Data Scientist's toolbox course within the Data Science Specialization. This publication is intended as a learning resource, all answers are documented and explained.

###Questions
<hr>
<font size="+2">1.  </font> Which of the following commands will create a directory called data in your current working directory?

<hr>

<font size="+1">

* mkdir data

</font>

<hr>

#####Explanation:

Creates directory in working directory.

```{r Question 1}

```

<hr>

<font size="+2">2.  </font> Which of the following will initiate a git repository locally?

<hr>

<font size="+1">

* git init

</font>

<hr>
```{r Question 2}

```

#####Explanation:

Initiaties local repository.

<hr>

<font size="+2">3.  </font> Suppose you have forked a repository called datascientist on Github but it isn't on your local computer yet. Which of the following is the command to bring the directory to your local computer?

<hr>

<font size="+1">

* git clone https://github.com/username/datascientist.git

</font>

<hr>
```{r Question 3}

```

#####Explanation:

If you don't have a local copy of the repo you use the clone command to create a new directory and remote tracking branches fro each branch. The pull command is used to update repos that are already local.

<hr>

<font size="+2">4.  </font> Which of the following will create a markdown document with a secondary heading saying "Data Science Specialization" and an unordered list with the following for bullet points: Uses R, Nine courses, Goes from raw data to data products

<hr>

<font size="+1">

* "## Data Science Specialization

* Uses R

* Nine courses

* Goes from raw data to data products"

</font>

<hr>
```{r Question 4}

```

#####Explanation:

Self-explanatory

<hr>

<font size="+2">5.  </font> Install and load the KernSmooth R package. What does the copyright message say?

<hr>

<font size="+1">

* Copyright M. P. Wand 1997-2009

</font>

<hr>

#####Explanation:
Run code:

```{r Question 5}
require(KernSmooth)
```


<hr>
Website: <http://www.ryantillis.com/>
